---
title: "Estimating the elimination feasibility in the 'end game' of control efforts for parasites subjected to regular mass drug administration: methods and their application to schistosomiasis"
author: "Chris Hoover"
geometry: margin = 0.5in
output: 
  pdf_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document sources files that contain functions and links to datasets produced by simulations to reproduce all figures presented in the main text of the paper  

# Figure 1: The $R_{eff}$ Profile and Figure 2: $BBR$ & $\frac{dW}{dt}$ 
```{r figs1_2, warnings = FALSE}
#load functions and models
source("Reff_BBR_fns.R")
source("schisto_mods_pdd_nopdd.R")

#Load parameter sets and eqbm values from Get_eqbm_for_trans_parameter_sets.R script
load("Outputs_Refs/model_fit_profile_likelihood_parameters.Rdata")
load("Outputs_Refs/best_fit_params.Rdata")

source("Reff_addNDDs_BBR_plots.R")
```

```{r save_figs1_2, eval=FALSE, include=FALSE}
#Save plot as high res tiff ##################
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig1.tiff", height = 11, width = 19.05, units = 'cm', 
     compression = "lzw", res = 300)
plot(log(W.seq), Reff.seq, type = 'l', lwd = 3, 
     ylim = c(0,3), xlim = log(c(min(W.seq)+0.003, max(W.seq))),
     xaxt = 'n', yaxt = 'n', ylab = '', xlab = '')  
abline(h = 1, lty=3, lwd = 2)
#abline(h = max(r0.seq), lty = 3, col = 2)
lines(log(W.seq), r0.seq, lty = 2, lwd = 3)

segments(x0 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]),
         x1 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]), #col = 3,
         y0 = 1, y1 = -1, lty = 2, lwd = 2)
segments(x0 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8]),
         x1 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8]), #col = 3,
         y0 = 1, y1 = -1, lty = 2, lwd = 2)
segments(x0 = log(W.seq[which(Reff.seq == max(Reff.seq))]),
         x1 = log(W.seq[which(Reff.seq == max(Reff.seq))]), #col = 3,
         y0 = max(Reff.seq), y1 = -1, lty = 2, lwd = 2)

axis(1, at = c(log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]), 
               log(W.seq[which(Reff.seq == max(Reff.seq))]),
               log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8])),
     labels = c(expression(paste(italic('W'[bp]), sep = '')),
                expression(paste(italic(' W'[peak]), sep = '')),
                expression(paste(italic(' W'[eq]), sep = ''))), #col = 3,
     lty = 2,  mgp = c(3,1,0), cex.axis = 1.2)
axis(1, at = c(-4,0,4), mgp = c(3,1.2,0), cex.axis = 1.2)
axis(2, at = max(r0.seq), labels = expression(paste(italic('R'[0]), sep = '')), #col = 2, 
     lty=2, las = 2, mgp = c(3,0.75,0), cex.axis = 1.2)
axis(2, at = c(0,1,2,3), labels = c('0', '1', '2', '3'), cex.axis = 1.2)

mtext(side = 2, text = expression(paste('R'[eff], sep = '')), line = 2.5, cex = 1.4)
mtext(side = 1, text = expression(paste('     log (', italic('W'), ')', sep = '')),
      line = 3, cex = 1.4)
dev.off()

#Save fig 2 as high resolution tiff ########
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig2.tiff", height = 14.5, width = 19.05, units = 'cm', 
     compression = "lzw", res = 300)

par(mar=c(4.6,6.6,1.1,0.6))    

layout(matrix(c(1,1,1,1,1,1,1,1,1,1,
                1,1,1,1,1,1,1,1,1,1,
                1,1,1,1,1,1,1,1,1,1,
                1,1,1,1,1,1,1,1,1,1,
                2,2,2,2,2,2,2,2,2,2,
                2,3,3,3,3,2,2,2,2,2,
                2,3,3,3,3,2,2,2,2,2,
                2,3,3,3,3,2,2,2,2,2,
                2,2,2,2,2,2,2,2,2,2,
                2,2,2,2,2,2,2,2,2,2), 
                10, 10, byrow = TRUE))
  
plot(log(W.seq), (dwdt.seq*365)/W.seq, type='l', lwd=3, ylim=c(-1, 1.2), xlim =c(-4.3, log(max(W.seq))),
     ylab="", xaxt = 'n', yaxt ='n', xlab = '')
    abline(h = 0, lty=3, lwd = 2)
    lines(log(W.seq), (dwdt.seq2*365)/W.seq, lwd = 3, lty = 2)
    
    segments(x0 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]),
             x1 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]), #col = 3,
             y0 = 0, y1 = -1, lty = 2, lwd = 2)
    segments(x0 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8]),
             x1 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8]), #col = 3,
             y0 = 0, y1 = -1, lty = 2, lwd = 2)
    segments(x0 = log(W.seq[which(Reff.seq == max(Reff.seq))]),
             x1 = log(W.seq[which(Reff.seq == max(Reff.seq))]), #col = 3,
             y0 = max((dwdt.seq*365)/W.seq), y1 = -1, lty = 2, lwd = 2)
    
    axis(1, at = c(log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]), 
                   log(W.seq[which(Reff.seq == max(Reff.seq))]),
                   log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][8])),
         labels = c(expression(paste(italic('W'[bp]), sep = '')),
                    expression(paste(italic(' W'[peak]), sep = '')),
                    expression(paste(italic('    W'[eq]), sep = ''))), #col = 3,
         lty = 2,  mgp = c(3,1.2,0), cex.axis = 1.25)
    axis(1, at = c(-4,0,4), mgp = c(3,1.4,0), cex.axis = 1.25)
    axis(2, at = c(-1, -0.5,  -0.25, 0, 0.25,  0.5, 1), cex.axis = 1.25, 
         labels = c('-1.0', '-0.5',  '', '0', '',  '0.5', '1.0'), mgp = c(3,0.75,0))
    
    mtext(side = 2, text = expression(italic(BBR)), line = 2.75, cex = 1.5)
    text(x=5.25, y=0.99, labels='a', pos=1, cex=3)
    
        
#plot dwdt trajectories ############
plot(log(W.seq), dwdt.seq, type = 'l', lwd = 3, ylim = c(-0.002, 0.035), xlim = c(min(log(W.seq)), 4.5),
     xaxt = 'n', yaxt = 'n', ylab = '', xlab = '')
    
    mtext(side = 1, text = expression(paste(' log (', italic('W'), ')', sep = '')), line = 3.5, cex = 1.5)
    mtext(side = 2, text = expression(paste(italic(frac(dW, dt)))), line = 1.75, cex = 1.5)
    
    axis(1, at = c(-4,0,4), mgp = c(3,1,0), cex.axis = 1.25)
    axis(2, at = c(-0.002,0,0.002,0.004,0.006,0.008, 0.01, 0.02, 0.03),
         labels = c('-0.002','0','0.002', '', '0.006','0.008','0.01', '0.02', '0.03'), 
         mgp = c(3,0.75,0), cex.axis = 1.25)
    
    lines(log(W.seq), dwdt.seq2, lwd = 3, lty = 2)
    text(x=4.4, y=0.03, labels='b', pos=1, cex=3)
    legend(x = 1.5, y = 0.0075, legend = c(expression(italic(PDD-free)), expression(italic(PDD))),
           lwd = 2, lty = c(2,1), bty = 'n', cex = 1.25)
    
#zoom to y axis ##########
plot(log(W.seq), dwdt.seq, type = 'l', lwd = 3, xaxt = 'n', yaxt = 'n', bty = 'n', xlab = '',
     ylab = '', #xlab = expression(paste('log (', italic('W'), ')', sep = '')),
     ylim = c(-0.0002, 0.0002), xlim = c(-4,-1))

    #mtext(side = 2, text = expression(paste(italic(frac(dW, dt)))), line = 1.5)
    axis(1, at = c(-4,-3,-1), mgp = c(3,1,0), cex.axis = 1.25)
    axis(2, at = c(-0.0002, 0,0.0002),
         labels = c('-0.0002',  '0', '0.0002'),
         mgp = c(3,0.75,0), cex.axis = 1.25)
    
    
    segments(x0 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]),
             x1 = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]), #col = 3,
             y0 = 0, y1 = -1, lty = 2, lwd = 2)
    
    axis(1, at = log(W.seq[which(round(Reff.seq, digits = 2) == 1.0)][1]),
         labels = expression(paste(italic('   W'[bp]), sep = '')),
         lty = 2,  mgp = c(3,1.4,0), cex.axis = 1.25)
    
    abline(h = 0, lty=3, lwd = 2)
    lines(log(W.seq), dwdt.seq2, lwd = 2, lty = 2)

par(opar)    
dev.off()

```

# Figures 3 and 4: Estimation of BBR from worm burden and prevalence data   
```{r figs3_4, warnings = FALSE}
#Takes outputs from PDD_noPDD_sims that are saved in outputs_refs folder 
# and uses them to produce Figs 3 and 4
source("PDD_noPDD_plots_analyze.R")
```

```{r save_figs3_4, eval = FALSE, include = FALSE}
#Save Fig 3 as tiff
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig3.tiff", height = 14, width = 19.05, units = 'cm', 
     compression = "lzw", res = 300) 
  multiplot(w.ggp, bbr.ggp, eps.ggp, layout = matrix(c(1,1,2,3), nrow = 2, byrow = T))
  
dev.off()

#Save Fig 4 as tiff
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig3_prev.tiff", height = 14, width = 19.05, units = 'cm', 
     compression = "lzw", res = 300) 
  multiplot(prev.ggp, bbr_prev.ggp, eps_prev.ggp, layout = matrix(c(1,1,2,3), nrow = 2, byrow = T))
  
dev.off()

```

# Figure 5:Scatter plot from stochastic model   
```{r fig5, warnings = FALSE}
#Takes output from stochastic model simulations found in Savio/Runs
# which simulate the stochastic model over a range of transmission intensities and clumping parameters
#Plots some additional 
source("stochModSims_postProcess.R")
```

```{r other_plots, eval = FALSE, include = FALSE}
#other plots #######  
#prevalence based
plot(par.mat2$eps.prev, par.mat2$pe, pch = 18, cex = 0.6, ylim = c(0,1),
     xlab = expression(epsilon), ylab = expression(italic('P(e)')))
 
#logit transform p(e)
plot(par.mat0_1$eps, log(par.mat0_1$pe / (1 - par.mat0_1$pe)), 
     pch = 18, cex = 0.6, #ylim = c(0,1),
     xlab = expression(epsilon), ylab = expression(italic('P(e)')))
 abline(a = pe.mod$coefficients[1], b = pe.mod$coefficients[2],
        lty = 2, col = 2, lwd = 2)

#plot relationship between eps and its standard deviation
plot(par.mat2$eps, par.mat2$eps.sd, pch = 18, cex = 0.6, #ylim = c(0,1),
     ylab = expression(paste(epsilon, ' St. Dev.', sep='')), 
     xlab = expression(epsilon))

#p(e) across transmission intensity
plot(par.mat2$lam, par.mat2$pe, pch = 18, cex = 0.6, ylim = c(0,1),
     xlab = expression(lambda), ylab = expression(italic('P(e)')))

#p(e) across pos. dens. dep.
plot(par.mat2$kap, par.mat2$pe, pch = 18, cex = 0.6, ylim = c(0,1),
     xlab = expression(kappa), ylab = expression(italic('P(e)')))

#plot regression prediction with actual data #########
  plot(par.mat0_1$eps, par.mat0_1$pe, pch = 18, cex = 0.6, ylim = c(0,1),
       xlab = expression(epsilon), ylab = expression(italic('P(e)')))
  
  back.trans = function(eps){
    p = exp(pe.mod$coefficients[1] + eps*pe.mod$coefficients[2])
    pe.pred = p / (1+p)
    return(pe.pred)
  }
    lines(seq(-0.05, 0.02, by = 0.001), sapply(seq(-0.05, 0.02, by = 0.001), back.trans, simplify = T),
          lty = 2,col = 2, lwd = 2)


#surface of p(e) across kappa and lambda
lams = unique(par.mat2$lam)
kaps = unique(par.mat2$kap)

lkmat = matrix(par.mat2$pe, ncol=50, nrow=50, byrow = T)

persp(y = lams, ylim = range(lams), x = kaps, xlim = range(kaps),
      z = lkmat, ticktype = 'detailed', nticks = 4, 
      xlab = 'Pos. Density Dependence',
      ylab = 'Transmission Intensity',
      zlab = 'Probability of Elimination',
      phi = 20, theta = 135, shade = 0.4, col = 'lightblue')

```


```{r save_fig5, eval = FALSE, include = FALSE}
#Save plot as tiff
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig5.tiff", 
     height = 13.2, width = 13.2, units = 'cm', compression = "lzw", res = 300) 
par.mat2 %>% 
  ggplot(aes(x = eps, y = pe)) + geom_point(pch = 18, cex = 0.8) + 
    labs(x = expression(epsilon), 
         y = expression(italic('P(e)'))) +
    theme_bw()
dev.off()
```

# Figure 6: Sensitivity of Epsilon to transmission intensity and clumping parameter  
```{r}
source("eps_surface_kap_lam_plots.R")
```

```{r fig_6_save, eval = FALSE, include = FALSE}
#Save as tiff ###########
tiff("Elimination_Feasibility/plots/PLoS_Figs_PostReview/Fig5.tiff", 
     height = 13.2, width = 13.2, units = 'cm', compression = "lzw", res = 300) 

persp(y = lam.range, ylim = range(lam.range), x = kap.range, xlim = range(kap.range),
      z = eps.fill, zlim = c(-0.05, 0.05), ticktype = 'detailed', nticks = 4, 
      xlab = 'Pos. Density Dependence',
      ylab = 'Transmission Intensity',
      zlab = 'Elimination Feasibility Estimator',
      phi = 18, theta = 45, shade = 0.4, cex.lab = 0.75, cex.axis = 0.5)

dev.off()

rm(list = ls())

```

